Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-17 icmssp-paper/parts/04_results.tex
[WIP] Shortening introduction
Rewrite Chapter 1 for conference paper

\section{Preliminary Results and Discussion}
The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems. During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e. the results vary drastically every time the same tests were done). This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.

@@

\begin{table}[h]
	\centering
	\caption{Image negation under Paillier}
	\label{tbl:neg-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
    \end{tabular}
\end{table}
% \begin{table}[h]
% 	\centering
% 	\caption{Image negation under Dasgupta--Pal}
% 	\label{tbl:neg-dp}
%     \begin{tabular}{lcccccc}
%         \toprule
%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
% 		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
% 		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
% 		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
% 		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
% 		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
% 		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
% 		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
% 		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
% 		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
% 		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\
% 		\bottomrule
%         \end{tabular}
% \end{table}
\begin{table}[h]
	\centering
	\caption{Image negation under DGK}
	\label{tbl:neg-dgk}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 0.000 & $\infty$ & 1.00000 & 0.509 & 0.011 & 0.450 \\
		(b) & 0.000 & $\infty$ & 1.00000 & 0.512 & 0.009 & 0.462 \\
		(c) & 0.000 & $\infty$ & 1.00000 & 0.732 & 0.018 & 0.519 \\
		(d) & 0.000 & $\infty$ & 1.00000 & 0.593 & 0.017 & 0.677 \\
		(e) & 0.000 & $\infty$ & 1.00000 & 0.607 & 0.010 & 0.454 \\
		(f) & 0.000 & $\infty$ & 1.00000 & 0.550 & 0.010 & 0.507 \\
		(g) & 0.000 & $\infty$ & 1.00000 & 0.532 & 0.010 & 0.471 \\
		(h) & 0.000 & $\infty$ & 1.00000 & 0.538 & 0.010 & 0.513 \\
		(i) & 0.000 & $\infty$ & 1.00000 & 0.606 & 0.010 & 0.519 \\
		(j) & 0.000 & $\infty$ & 1.00000 & 0.608 & 0.012 & 0.496 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Logarithm transformation under Paillier}
	\label{tbl:log-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
% \begin{table}[h]
% 	\caption{Logarithm transformation under Dasgupta--Pal}
% 	\label{tbl:log-dp}
%     \begin{tabular}{lcccccc}
%         \toprule
%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
% 		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
% 		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
% 		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
% 		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
% 		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
% 		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
% 		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
% 		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
% 		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
% 		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
% 		\bottomrule
%         \end{tabular}
% \end{table}
\begin{table}[h]
	\caption{Logarithm transformation under DGK}
	\label{tbl:log-dgk}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
		\bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

% \begin{table}[h]
% 	\centering
% 	\caption{Power-law transformation under Dasgupta--Pal}
% 	\label{tbl:pwr-dp}
%     \begin{tabular}{lcccccc}
%         \toprule
%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
% 		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
% 		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
% 		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
% 		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
% 		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
% 		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
% 		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
% 		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
% 		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
% 		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
% 		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
% 		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
% 		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
% 		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
% 		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
% 		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
% 		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
% 		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
% 		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
% 		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
% 		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
% 		\bottomrule
%         \end{tabular}
% \end{table}
\begin{table}[h]
	\centering
	\caption{Power-law transformation under DGK}
	\label{tbl:pwr-dgk}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
		\bottomrule
    \end{tabular}
\end{table}

>>>>

\section{Preliminary Results and Discussion}
\label{sec:chapter_4}
The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems. During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e. the results vary drastically every time the same tests were done). This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.

@@

\begin{table}[ht]
	\centering
	\caption{Image negation under Paillier}
	\label{tbl:neg-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
    \end{tabular}
\end{table}
% \begin{table}[h]
% 	\centering
% 	\caption{Image negation under Dasgupta--Pal}
% 	\label{tbl:neg-dp}
%     \begin{tabular}{lcccccc}
%         \toprule
%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
% 		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
% 		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
% 		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
% 		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
% 		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
% 		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
% 		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
% 		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
% 		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
% 		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\
% 		\bottomrule
%         \end{tabular}
% \end{table}
\begin{table}[ht]
	\centering
	\caption{Image negation under DGK}
	\label{tbl:neg-dgk}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 0.000 & $\infty$ & 1.00000 & 0.509 & 0.011 & 0.450 \\
		(b) & 0.000 & $\infty$ & 1.00000 & 0.512 & 0.009 & 0.462 \\
		(c) & 0.000 & $\infty$ & 1.00000 & 0.732 & 0.018 & 0.519 \\
		(d) & 0.000 & $\infty$ & 1.00000 & 0.593 & 0.017 & 0.677 \\
		(e) & 0.000 & $\infty$ & 1.00000 & 0.607 & 0.010 & 0.454 \\
		(f) & 0.000 & $\infty$ & 1.00000 & 0.550 & 0.010 & 0.507 \\
		(g) & 0.000 & $\infty$ & 1.00000 & 0.532 & 0.010 & 0.471 \\
		(h) & 0.000 & $\infty$ & 1.00000 & 0.538 & 0.010 & 0.513 \\
		(i) & 0.000 & $\infty$ & 1.00000 & 0.606 & 0.010 & 0.519 \\
		(j) & 0.000 & $\infty$ & 1.00000 & 0.608 & 0.012 & 0.496 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[ht]
	\centering
	\caption{Logarithm transformation under Paillier}
	\label{tbl:log-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
% \begin{table}[h]
% 	\caption{Logarithm transformation under Dasgupta--Pal}
% 	\label{tbl:log-dp}
%     \begin{tabular}{lcccccc}
%         \toprule
%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
% 		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
% 		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
% 		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
% 		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
% 		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
% 		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
% 		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
% 		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
% 		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
% 		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
% 		\bottomrule
%         \end{tabular}
% \end{table}
\begin{table}[ht]
	\caption{Logarithm transformation under DGK}
	\label{tbl:log-dgk}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
		\bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[ht]
	\centering
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

% \begin{table}[h]
% 	\centering
% 	\caption{Power-law transformation under Dasgupta--Pal}
% 	\label{tbl:pwr-dp}
%     \begin{tabular}{lcccccc}
%         \toprule
%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
% 		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
% 		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
% 		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
% 		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
% 		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
% 		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
% 		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
% 		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
% 		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
% 		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
% 		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
% 		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
% 		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
% 		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
% 		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
% 		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
% 		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
% 		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
% 		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
% 		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
% 		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
% 		\bottomrule
%         \end{tabular}
% \end{table}
\begin{table}[ht]
	\centering
	\caption{Power-law transformation under DGK}
	\label{tbl:pwr-dgk}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
		\bottomrule
    \end{tabular}
\end{table}
